---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `rgudhi`

<!-- badges: start -->
[![check-standard](https://github.com/LMJL-Alea/rgudhi/workflows/R-CMD-check/badge.svg)](https://github.com/LMJL-Alea/rgudhi/actions)
[![test-coverage](https://github.com/LMJL-Alea/rgudhi/workflows/test-coverage/badge.svg)](https://github.com/LMJL-Alea/rgudhi/actions)
[![Codecov test coverage](https://codecov.io/gh/LMJL-Alea/rgudhi/branch/master/graph/badge.svg)](https://app.codecov.io/gh/LMJL-Alea/rgudhi?branch=master)
[![pkgdown](https://github.com/LMJL-Alea/rgudhi/workflows/pkgdown/badge.svg)](https://github.com/LMJL-Alea/rgudhi/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/rgudhi)](https://CRAN.R-project.org/package=rgudhi)
<!-- badges: end -->

The goal of `rgudhi` is to provide an R interface to the Python package [gudhi](https://gudhi.inria.fr/python/latest/). The [GUDHI](https://gudhi.inria.fr) library is a generic open source C++ library, with a Python interface, for Topological Data Analysis (TDA) and Higher Dimensional Geometry Understanding. The library offers state-of-the-art data structures and algorithms to construct simplicial complexes and compute persistent homology.

## Installation

You can install the development version of `rgudhi` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LMJL-Alea/rgudhi")
```

## Example: Persistence diagram using an Alpha complex

```{r example}
library(rgudhi)
n <- 10
X <- seq_circle(n)
ac <- AlphaComplex$new(points = X)
st <- ac$create_simplex_tree()
st$persistence()
```
